Figures

### 2017-01-13 figures/partnerSIR.tex
fix arrowheads

\newcommand{\pairformepcinf}{
	\draw[->, purple, dashed, very thick] (I)
		to [bend right=45] (StoI);
	\draw[->, red, dashed, very thick] (SI)
		to  (StoI);
	\draw[->, red, dashed, very thick] (SI)
		to [bend right=45] (SStoSI);
	\draw[->, red, dashed, very thick] (II)
		to [bend left=60] (SStoSI);
	\draw[->, purple, dashed, very thick] (I)
		to  (SItoII);
	\draw[->, red, dashed, very thick] (II)
		to [bend left=70] (SItoII);
%% these are the problematic ones
% does this help?
%   http://tex.stackexchange.com/questions/209942/curved-arrows-in-tikz
% http://tex.stackexchange.com/questions/40388/avoid-arrow-crossing-over-blocks-in-flow-chart
         \draw[->, red, dashed, very thick] plot [smooth, tension=0.4] coordinates
            { (II.north) ([xshift=0.2cm,yshift=0.2cm]I.north east) ([xshift=-0.5cm,yshift=0.2cm]I.north west) (StoI) } (StoI);
            \draw[->, purple, dashed, very thick] plot [smooth] coordinates {
             ([yshift=0.3cm]I.west) ([xshift=0.5cm,yshift=0.5cm]S.north east)
             ([xshift=-0.2cm,yshift=0.2cm]S.north west) 
             ([xshift=0.5cm,yshift=0.5cm]SS.north east)
             (SStoSI) } (SStoSI);

>>>>

\newcommand{\pairformepcinf}{
	\draw[->, purple, dashed, very thick] (I)
		to [bend right=45] (StoI);
	\draw[->, red, dashed, very thick] (SI)
		to  (StoI);
	\draw[->, red, dashed, very thick] (SI)
		to [bend right=45] (SStoSI);
	\draw[->, red, dashed, very thick] (II)
		to [bend left=60] (SStoSI);
	\draw[->, purple, dashed, very thick] (I)
		to  (SItoII);
	\draw[->, red, dashed, very thick] (II)
		to [bend left=70] (SItoII);
%% these are the problematic ones
% does this help?
%   http://tex.stackexchange.com/questions/209942/curved-arrows-in-tikz
% http://tex.stackexchange.com/questions/40388/avoid-arrow-crossing-over-blocks-in-flow-chart
         \draw[->, red, dashed, very thick] plot [smooth, tension=0.4] coordinates
            { (II.north) ([xshift=0.2cm,yshift=0.2cm]I.north east) 
              ([xshift=-0.5cm,yshift=0.2cm]I.north west) 
              ([yshift=0.25cm]StoI) }
              to (StoI) ;

            \draw[->, purple, dashed, very thick] plot [smooth] coordinates {
             ([yshift=0.3cm]I.west) ([xshift=0.5cm,yshift=0.5cm]S.north east)
             ([xshift=-0.2cm,yshift=0.2cm]S.north west) 
             ([xshift=0.5cm,yshift=0.5cm]SS.north east)
              %% hack to get arrows in the right direction
               ([yshift=0.25cm]SStoSI) } to (SStoSI);
